---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

# Importing Libraries and Dataset

```{r}
library(tidyverse)
AutoMobiles<-read.csv("C:/Users/saic3/CSE3046-F2-LAB_SLOT_L3+L4/Datasets/Automobile.csv")
```
#Check For Null Values:
```{r}
ToNull<-is.na(AutoMobiles$price)
sum(ToNull)
```
# Removing the NA Values
```{r}
AutoMobiles<-AutoMobiles%>%fill(price,.direction = "down")
sum(is.na(AutoMobiles$price))
```
# Question-1:Find last n rows with price > 14000? 
```{r AutoMobiles}
tail(AutoMobiles["price">14000])
```
# Question-2: Count the total company in the dataset?
```{r}
unique(AutoMobiles$company)%>%length()
unique(AutoMobiles$company)

```
# Question-3: Find all the rows with body-style sedan? 
```{r}
AutoMobiles%>%filter(body.style=="sedan")
AutoMobiles%>%filter(body.style=="sedan")%>%count()
```
# Question-4: Find the 3rd most expensive car price and company name. 
```{r}
Q4<-AutoMobiles%>%group_by(company)%>%summarise(newPrice=max(price))%>%arrange(desc(newPrice))
#Since Due to 0-based Indexing and No of Companies are 16 from the Q2 We Use 16-2 as Index
Q4[3,]
```
#Question-5: Find the most expensive car for each company. 
#Similar to Question 4 Where Finding the Third Highest Car Price and Its Company
```{r}
Q4
```
#Question 6: Print all Toyota cars details

```{r}
AutoMobiles%>%filter(company=="toyota")
```
# Question-7:Find the count of “convertible” type cars in “alfa-romero” company
```{r}
count(AutoMobiles%>%filter(company=="alfa-romero"&body.style=="convertible"))
```
```{r}
AutoMobiles%>%filter(company=="alfa-romero"&body.style=="convertible")
```
# Question-8: Create a vector with 20 numeric items and extract top 2 most frequent items of a vector? 
```{r}
numeric_vector<-c(1, 2, 3, 2, 1, 4, 5, 1, 2, 6, 7, 7, 8, 9, 3, 10, 5, 5, 2, 1)
item_freq <- table(numeric_vector)
# Sort the frequencies in decreasing order
sorted_freq <- sort(item_freq, decreasing = TRUE)
# Extract the top 2 most frequent items
top_2_items <- as.numeric(names(sorted_freq[1:2]))

print(top_2_items)
```
#Question-9:Create two dataframe with different attributes and merge them column wise. 
```{r}
df1<-data.frame(Students=c("Somu","Venu","Venkat","Sri","Charvi","Marky","Duplex"),Marks=c(10,100,49,40,15,21,95))
df1
```
```{r}
df2<-data.frame(Items=c("Rice","Cofee","Tea","Oil","Vegetables","Fruits","Ghee"),Prices=c(12,80,29,87,2,13,16))
df2
```
```{r}
df1<-cbind(df1,df2)
df1
```

#QUestion-10: Create two dataframe with the same attributes and merge them row wise. 
```{r}
df1<-data.frame(Students=c("Somu","Venu","Venkat","Sri","Charvi","Marky","Duplex"),Marks=c(10,100,49,40,15,21,95))
df3<-data.frame(Students=c("Sai","Kent","Bruce"),Marks=c(1000,1,99))
df1<-rbind(df1,df3)
df1

```

